Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-12 Article.tex
update figure 2

In more details, and as will be explained in section \ref{sec:model}, we consider agents that, depending on meteorological conditions, personal preferences, and their appliances (loads and generators), consume and produce more or less energy (using only wind turbines and PV as generators, which can be quite simply and efficiently modeled).  We used real meteorological traces (see section \ref{sec:model}) to account for seasonal and daily variations in the prosumers energetic output profiles as well as realistic geographical correlations. With these ingredients, we are able simulate the different production/consumption profiles.

@@

\begin{center}
\begin{figure}
\includegraphics[scale=0.45]{figure2.jpg}
\caption{Process diagram}
\label{Fig1}
\end{figure}
\end{center}

>>>>

In more details, and as will be explained in section \ref{sec:model}, we consider agents that depend on meteorological conditions, personal preferences, and their appliances (loads and generators), consume and produce more or less energy (using only wind turbines and PV as generators, which can be quite simply and efficiently modeled).  We used real meteorological traces (see section \ref{sec:model}) to account for seasonal and daily variations in the prosumers energetic output profiles as well as realistic geographical correlations. With these ingredients, we are able simulate the different production/consumption profiles.

@@

\begin{center}
\begin{figure}
\includegraphics[scale=0.45]{figure2/Fig2.pdf}
\caption{Process diagram}
\label{Fig1}
\end{figure}
\end{center}
